Conditions for $d$-local-connectedness of boundaries of hyperbolic groups

### 2020-01-15 paper.tex
Changed align*s to equation*s
To make qedhere work

  Notice that $\newdist$ agrees with $\dist$ on $G$, and for any $x$ and $y$ in
  $K$, if $x^\star$ and $y^\star$ are \emph{any} vertices of simplices
  containing $x$ and $y$ respectively, then
  \begin{align*}
    \abs{\newdist(x,y) - \dist(x^\star, y^\star)} \leq 2D
  \end{align*}
\end{remark}

@@

\begin{definition}
  Given points $x$, $y$ and $z$ in $K$, define the \emph{Gromov product
  $\gromov{x}{y}{z}$ of $x$, $y$ and $z$} as follows.
  \begin{align*}
    \gromov{x}{y}{z} = \frac{1}{2}\left(\newdist(x,y) + \newdist(x,z) -
          \newdist(y,z)\right)
  \end{align*}
\end{definition}

@@

\begin{definition}
  We define a topology on $K \union \boundary G$ by describing a neighbourhood
  basis of each point.
  \begin{enumerate}
    \item For $x \in K$, the neighbourhoods of $x$ are the neighbourhoods of
      $x$ in $K$, treating $K$ with the usual topology of a simplicial complex.
    \item For $\xi \in \boundary G$, the set
      \begin{align*}
        \set{x \in K \union \boundary G \suchthat \gromov{e}{x}{\xi} \geq N}_{N\in\naturals}
      \end{align*}
      is a fundamental system of neighbourhoods for the point $x$.
  \end{enumerate}
\end{definition}

@@

\begin{proof}
  Let $g_1, \dotsc, g_k \subset \Vertices(L_n)$ span a simplex in $L_n$, so 
  there exists a point $\xi \in \bigintersection_{i=1}^k V_n(g_i)$.  Let
  $\gamma_1, \dotsc, \gamma_n$ be geodesic rays with $\gamma_i(0) = e$,
  $\gamma_i(\infty) = \xi$ and $\dist(\gamma_i(n), g_i) \leq 2\delta+1$.
  Then $\Diam\set{\gamma_i(n) \suchthat i=1, \dotsc, n} \leq 2\delta$, and it
  follows that
  \begin{align*}
    \Diam\{g_1, \dotsc, g_k\} \leq 6\delta+ 2 \leq D.\qedhere
  \end{align*}
\end{proof}

For each $n$, fix a partition of unity subordinate to the open covering 
\begin{align*}
  \set{V_n(x) \suchthat x \in S_n}
\end{align*} 
of $\boundary G$. This is equivalent to a continuous map $\pi_n \from \boundary
G \to L_n$. Let $p^\infty_n\from\boundary G\to K_n$ be the composition of
$\pi_n$ with the simplicial map $L_n \to K_n$ given by
\cref{lem:L_Ksimplicial}.

@@

\begin{lemma}\label{lem:boundary_gromov_product}
  Let $\alpha_1$ and $\alpha_2$ be geodesic rays with $\alpha_1(0) =
  \alpha_2(0) = e$. Then for any $m_1$ and $m_2$,
  \begin{align*}
    \gromov{e}{\alpha_1(m_1)}{\alpha_2(m_2)} \geq 
        \min\{m_1 - 3\delta, m_2 - 3\delta, \gromov{e}{\alpha_1(\infty)}{\alpha_2(\infty)} - 6\delta\}
  \end{align*}
\end{lemma}

\begin{proof}
  By~\cite{bridsonhaefliger99},
  \begin{align*}
    \gromov{e}{\alpha_1(\infty)}{\alpha_2(\infty)} \leq \liminf_{n_1, n_2}
        \gromov{e}{\alpha_1(n_1)}{\alpha_2(n_2)} + 2\delta.
  \end{align*}
  Let $n_1 \geq m_1$ and $n_2 \geq m_2$.

@@

  If $p_1$ lies between $\alpha_2(n_2)$ and $p_1$ on $[\alpha_1(n_1),
  \alpha_2(n_2)]$ then, by considering the triangle with vertices $p_2$,
  $\alpha_2(m_2)$ and $\alpha_2(n_2)$, we see that $\dist(p_1, \alpha_2) \leq
  2\delta$. Therefore $\dist(\alpha_1(m_1), \alpha_2) \leq 3\delta$, and so
  \begin{align*}
    \gromov{e}{\alpha_1(m_1)}{\alpha_2(m_2)} \geq \min\{m_1, m_2\} - 3\delta
  \end{align*}
  and the result follows.

  Otherwise,
  \begin{align*}
    \dist(\alpha_1(n_1), \alpha_2(n_2)) = \dist(\alpha_1(n_1), p_1) +
        \dist(p_1, p_2) + \dist(p_2, \alpha_2(n_2)).
  \end{align*}
  Therefore,
  \begin{align*}
    \mathrlap{\gromov{e}{\alpha_1(n_1)}{\alpha_n(n_2)} - \gromov{e}{\alpha_1(m_1)}{\alpha_2(m_2)}}
    \quad\quad\phantom{{}={}}&\\
           &\mathllap{{}={}}\left(\dist(\alpha_1(m_1), \alpha_1(n_1)) - \dist(\alpha_1(m_1), p_1)\right) \\
           &+ \left(\dist(\alpha_1(m_1), \alpha_2(m_2)) - \dist(p_1, p_2)\right) \\
           &+ \left(\dist(\alpha_2(m_2), \alpha_2(n_2)) - \dist(p_2, \alpha_2(m_2))\right) \\
           &\mathllap{{}\leq{}} \delta+2\delta+\delta=4\delta 
  \end{align*}
  It follows that
  \begin{align*}
    \gromov{e}{\alpha_1(\infty)}{\alpha_2(\infty)} \leq \gromov{e}{\alpha_1(m_1)}{\alpha_2(m_2)} + 6\delta,
  \end{align*}
  which completes the proof.
\end{proof}

@@

  By definition of the visual metric, $\gromov{e}{\xi_1}{\xi_2} \geq
  \log_a(k_1/\rho_0)$. Therefore, by \cref{lem:boundary_gromov_product},
  \begin{align*}
    \gromov{e}{\alpha_1(n)}{\alpha_2(n)} \geq \min\{n - 3\delta, \log_a(k_1/\rho_0) - 6\delta\}.
  \end{align*}
  In particular,
  \begin{align*}
    \dist(\alpha_1(n), \alpha_2(n)) \leq \max\{6\delta, 12\delta - 2(\log(k_1/\rho_0) - n)\}
  \end{align*}
  and the result follows.
\end{proof}

@@

\begin{proof}
  By definition, $p^\infty_m(\xi)$ is contained in the simplex spanned by the set
  $\set{g \in S_m \suchthat \xi \in V_m(g)}$ and $p^n_m\composed p^\infty_n(\xi)$ is
  contained in the simplex spanned by $\{p^n_m(g) \suchthat g \in S_n \text{
  and } \xi \in V_n(g)\}$.  We show that the union
  \begin{align*}
    \set{g \in S_m \suchthat \xi \in V_m(g)} \union \{p^n_m(g) \suchthat g \in S_n \text{ and } \xi \in V_n(g)\}
  \end{align*}
  of these sets spans a simplex in $K_n$; this simplex then contains
  $p^\infty_m(\xi)$ and $p^n_m\composed p^\infty_n(\xi)$.  It is sufficient to
  prove that if $\xi \in V_m(g_1) \intersection V_n(g_2)$ for $g_1 \in S_m$ and
  $g_2 \in S_n$ then $\dist(g_1, p^n_m(g_2)) \leq D$.

@@

  The limit~\eqref{eqn:zi_closer_to_gi_than_x}, taken together with the fact
  that $\dist(g_i, x) = \dist(g_i, p_i) = n_i$, shows that the distances
  $\dist([z_i, g_i], x)$ and $\dist([z_i, g_i], p_i)$ tend to infinity as
  $i\to\infty$.  We now divide into cases according to which of $x$ and $p_i$
  is closer to $z_i$.
  \begin{enumerate}
    \item If $x$ is between $z_i$ and $p_i$ on $\alpha$ then by considering a
      geodesic triangle with vertices $g_i$, $z_i$ and $p_i$ we see that for
      $i$ sufficiently large, $x$ is within a distance $\delta$ of a point
      $q_i$ on the geodesic from $g_i$ to $p_i$.  Therefore,
      \begin{align*}
        \dist(g_i,x)&\leq \dist(g_i,q_i)+\delta\\
                        &\leq \dist(g_i,p_i)-\dist(p_i,q_i)+\delta\\
                        &\leq \dist(g_i,p_i)-\dist(x,p_i)+2\delta.
      \end{align*}
      It follows that $\dist(x,p_i) \leq \dist(g_i,p_i)-\dist(g_i,x)+2\delta
      = 2\delta$.
    \item If $p_i$ is between $z_i$ and $x$ on $\alpha$ then by an identical 
      argument with the r\^oles of $x$ and $p_i$ reversed we can similarly 
      deduce that 
      \begin{align*}
        \dist(x,p_i)\leq\dist(g_i,x) - \dist(g_i,p_i) + 2\delta =2\delta.
      \end{align*}
  \end{enumerate}

@@

  Since $g_i \to \xi$, the distance $\dist(v, [\xi, g_i]) \to \infty$ as
  $i\to\infty$. The triangle with vertices $\xi$, $g_i$ and $x$ is
  $\delta$-slim, so the geodesic path from $g_i$ to $x$ passes within a
  distance $\delta$ of $v$ for $i$ large enough. Therefore, since $\dist(g_i,
  x) = n_i$ for $i$ large enough, the following inequality holds for all $i$
  large enough.
  \begin{align*}
    0 \leq \dist(g_i, v) + \dist(v, x) - n_i \leq 2\delta.
  \end{align*}

@@

  We split into cases according to the order of $\xi$, $v'$ and $x'$ on
  $\alpha'$.
  \begin{enumerate}
    \item
      First we suppose that $v'$ is between $x'$ and $\xi$ on $\alpha'$. Then as
      in the argument above, for $i$ sufficiently large we have the following
      inequality:
      \begin{align*}
        0 \leq \dist(g_i, v') + \dist(v', x') - n_i \leq 2\delta.
      \end{align*}
      And therefore,
      \begin{align*}
        -2\delta \leq \dist(g_i, v) + \dist(v, x') - n_i \leq 4\delta.
      \end{align*}
      Finally, putting these inequalities together,
      \begin{align*}
        \dist(v,x') \leq \dist(v,x) + 4\delta,
      \end{align*}
      and thus we can uniformly bound this distance in this case.
    \item
      Alternatively, $x'$ is between $v'$ and $\xi$ on $\alpha'$ and so (since
      the triangle with vertices $\xi$, $v$ and $v'$ is $\delta$-slim) $x'$ is
      within a distance $2\delta$ of the geodesic ray from $x$ to $\xi$. By
      considering the triangle with vertices $\xi$, $g_i$ and $x$ for $i$ large
      enough, a geodesic segment from $g_i$ to $x$ passes within a distance
      $3\delta$ of $x'$. Therefore we have the following inequality for all $i$
      sufficiently large:
      \begin{align*}
        0 \leq \dist(g_i, x') + \dist(x', x) - \dist(g_i, x) \leq 6\delta.
      \end{align*}
      Finally, for $i$ sufficiently large, $\dist(g_i, x') = \dist(g_i, x) = n_i$,
      so
      \begin{align*}
        \dist(x,x') \leq 6\delta.
      \end{align*}
  \end{enumerate}
\end{proof}

@@

\begin{lemma}\label{lem:describing_q_i}\todo{Check this}
  Let $\zeta \in \boundary G - \set\xi$ and suppose that $q_i(\zeta) \in H_i$
  is defined, so $\zeta \in U_i$, and $N_{4\delta+1} q_i(\zeta) \in H_i$. Then
  $q_i(\zeta)$ is contained in the minimal simplex of $H_i$ with vertex set
  \begin{align*}
    N_{2\delta+1} \set{\eta(n_i)\suchthat\text{$\eta$ a geodesic ray with
    $\eta(0) = g_i$ and $\eta(\infty) = \zeta$}}.
  \end{align*}\qed
\end{lemma}

@@

\begin{lemma}\label{lem:propermaps} 
  For any compact subset $C \subset H$ there exists $i_0$ such that
  \begin{align*}
    \bigunion_{i\geq i_0} q_i^{-1} C
  \end{align*}
  is a relatively compact subset of $\boundary G - \set\xi$.
\end{lemma}

@@

\begin{restatable}{theorem}{ddagimpliesLCd}
  If $G$ satisfies $\Sd_M$ for all $M$ then $\boundary G$ is locally simply
  connected.
\end{restatable}

@@

\begin{lemma}\label{lem:useful}
  Let $(x_n)$ be a sequence of points in $G$ with $\dist(x_{n+1}, e) = 
  \dist(x_n, e) + 1$ and $\dist(x_{n+1}, x_n)$ bounded. Then,
  \begin{align*}
    \gromov{e}{x_m}{x_n} \geq \dist(e,x_m) - C
  \end{align*}
  for some constant $C$ depending only on $\delta$ and the bound on 
  $\dist(x_{n+1}, x_n)$.
\end{lemma}

@@

  By the triangle inequality it follows that for $n\geq m$ we have the following 
  inequality.
  \begin{align*}
    \vdistance(\alpha_n(\infty), \alpha_m(\infty)) \leq C_1 a^{-i_m}
  \end{align*}
  for some constants $C_1$ depending only on $\delta$ and $C_0$. Then, by
  definition of the visual metric, there exists a constant $C_2$ such that
  \begin{align*}
    \gromov{e}{\alpha_n(\infty)}{\alpha_m(\infty)} \geq i_m - C_2.
  \end{align*}

  Now, by \cref{lem:boundary_gromov_product} there exists a constant $C_3$ such
  that
  \begin{align*}
    \gromov{e}{\alpha_n(i_n)}{\alpha_m(i_m)} \geq i_m - C_3,\qedhere
  \end{align*}
  as required.
\end{proof}

\begin{lemma}\label{lem:linearproduct}
  There is a constant $C$ such that if $x \in \Skel_{d+1} K_m$ then
  \begin{align*}
    \gromov{e}{i^m_n(x)}{x} \geq m - C
  \end{align*}
  for all $n\geq m\geq n_0$.
\end{lemma}

@@

  We now bound the distance $\dist(y_n, y_{n+1}$. To start with, $\dist(y_n,
  i^n_{n+1} y_n) \leq \epsilon$. Let $R$ be such that any two vertices in the
  1-skeleton of $\sd^k \Delta^{d+1}$ are joined by a path traversing at most
  $R$ edges. Let $\sigma$ be the minimal simplex of $K_n$ containing
  $i^m_n(x)$. Then $y_n$ is a vertex of $\sigma$ and $y_{n+1}$ is a vertex of
  the image of $\sigma$ under $i^n_{n+1}$, so $\dist(i^n_{n+1} y_n, y_{n+1})
  \leq RD$.  Putting this together,
  \begin{align*}
      \dist(y_n, y_{n+1}) \leq \epsilon + RD
  \end{align*}

@@

  Finally, by applying the inequality in \cref{rem:dist_vs_newdist}, we deduce
  that
  \begin{align*}
      \gromov{e}{i^m_n(x)}{x} \geq m - C - 3D.\qedhere
  \end{align*}
\end{proof}

@@

\begin{lemma}\label{lem:simplexproduct}
  There is a constant $C$ such that if $m \geq n_0$ and $x$ and $y$ are in a
  common simplex of $\Skel_{d+1} K_m$ then
  \begin{align*}
    \gromov{e}{i^m_n(x)}{i^m_n(y)} \geq m - C
  \end{align*}
  for all $n\geq m$.
\end{lemma}

@@

\begin{proposition}\label{prop:basic_homotopies}
  Let $C$ be a constant. Then there exists a number $m_0$ and a function $\mu
  \from \posreals\to\posreals$ such that $\mu(\eta)\to0$ as $\eta\to0$ with the following
  property. Let $n \geq m_0$ and let $f_0$ and $f_1$ be any maps from
  $\boundary\Delta^{d+1}$ to $K_n$ satisfying the following conditions:
  \begin{enumerate}
    \item the maps $f_0$ and $f_1$ are affine on some subdivision of
      $\boundary\Delta^{d+1}$;
    \item for any $x \in \boundary\Delta^{d+1}$, the distance 
      $\newdist(f_0(x), f_1(x))$ is at most $C$;
    \item each of $f_0$ and $f_1$ admits a factoring.
  \end{enumerate}
  Then there is a homotopy $h$ from $i^n_\infty\composed f_0$ to
  $i^n_\infty\composed f_1$ satisfying a uniform continuity condition: for any
  $x \in \boundary\Delta^{d+1}$ and any $s$ and $t$ in $[0,1]$,
  \begin{align*}
    \rho(h(x,s), h(x,t)) \leq \mu(\abs{s-t})a^{-n}.
  \end{align*}
\end{proposition}

@@

  Let $n \geq m_0$.  Let $J$ be a subdivision of $\boundary\Delta^{d+1}$ such
  that $f_0$ and $f_1$ are both affine on $J$. Then the map 
  \begin{align*}
    f_0 \disjointunion f_1 \from J \times \{0\} \disjointunion J \times \{1\}
          \to K_n,
  \end{align*}
  defined on a subset of the product simplicial complex $J \times [0,1]$,
  satisfies the conditions of \cref{prop:extendingaffinemaps2}, and so admits
  an affine extension $F \from \sd^{k'} (J \times [0,1]) \to K_n$. Let $h =
  i^n_\infty \composed F$, so $h$ is a homotopy from $i^n_\infty\composed f_0$
  to $i^n_\infty\composed f_1$ and it remains to prove the uniform continuity
  assertion.

@@

\begin{proof}
  Let $\xi \in \boundary G$. By \cref{lem:linearproduct} there is a 
  constant $C$ such that 
  \begin{align*}
    \gromov{e}{i^m_n\composed p^\infty_m(\xi)}{p^\infty_m(\xi)} \geq m - C
  \end{align*} 
  for each $n\geq m\geq n_0$.

>>>>

  Notice that $\newdist$ agrees with $\dist$ on $G$, and for any $x$ and $y$ in
  $K$, if $x^\star$ and $y^\star$ are \emph{any} vertices of simplices
  containing $x$ and $y$ respectively, then
  \begin{equation*}
    \abs{\newdist(x,y) - \dist(x^\star, y^\star)} \leq 2D
  \end{equation*}
\end{remark}

@@

\begin{definition}
  Given points $x$, $y$ and $z$ in $K$, define the \emph{Gromov product
  $\gromov{x}{y}{z}$ of $x$, $y$ and $z$} as follows.
  \begin{equation*}
    \gromov{x}{y}{z} = \frac{1}{2}\left(\newdist(x,y) + \newdist(x,z) -
          \newdist(y,z)\right)
  \end{equation*}
\end{definition}

@@

\begin{definition}
  We define a topology on $K \union \boundary G$ by describing a neighbourhood
  basis of each point.
  \begin{enumerate}
    \item For $x \in K$, the neighbourhoods of $x$ are the neighbourhoods of
      $x$ in $K$, treating $K$ with the usual topology of a simplicial complex.
    \item For $\xi \in \boundary G$, the set
      \begin{equation*}
        \set{x \in K \union \boundary G \suchthat \gromov{e}{x}{\xi} \geq N}_{N\in\naturals}
      \end{equation*}
      is a fundamental system of neighbourhoods for the point $x$.
  \end{enumerate}
\end{definition}

@@

\begin{proof}
  Let $g_1, \dotsc, g_k \subset \Vertices(L_n)$ span a simplex in $L_n$, so 
  there exists a point $\xi \in \bigintersection_{i=1}^k V_n(g_i)$.  Let
  $\gamma_1, \dotsc, \gamma_n$ be geodesic rays with $\gamma_i(0) = e$,
  $\gamma_i(\infty) = \xi$ and $\dist(\gamma_i(n), g_i) \leq 2\delta+1$.
  Then $\Diam\set{\gamma_i(n) \suchthat i=1, \dotsc, n} \leq 2\delta$, and it
  follows that
  \begin{equation*}
    \Diam\{g_1, \dotsc, g_k\} \leq 6\delta+ 2 \leq D.\qedhere
  \end{equation*}
\end{proof}

For each $n$, fix a partition of unity subordinate to the open covering 
\begin{equation*}
  \set{V_n(x) \suchthat x \in S_n}
\end{equation*} 
of $\boundary G$. This is equivalent to a continuous map $\pi_n \from \boundary
G \to L_n$. Let $p^\infty_n\from\boundary G\to K_n$ be the composition of
$\pi_n$ with the simplicial map $L_n \to K_n$ given by
\cref{lem:L_Ksimplicial}.

@@

\begin{lemma}\label{lem:boundary_gromov_product}
  Let $\alpha_1$ and $\alpha_2$ be geodesic rays with $\alpha_1(0) =
  \alpha_2(0) = e$. Then for any $m_1$ and $m_2$,
  \begin{equation*}
    \gromov{e}{\alpha_1(m_1)}{\alpha_2(m_2)} \geq 
        \min\{m_1 - 3\delta, m_2 - 3\delta, \gromov{e}{\alpha_1(\infty)}{\alpha_2(\infty)} - 6\delta\}
  \end{equation*}
\end{lemma}

\begin{proof}
  By~\cite{bridsonhaefliger99},
  \begin{equation*}
    \gromov{e}{\alpha_1(\infty)}{\alpha_2(\infty)} \leq \liminf_{n_1, n_2}
        \gromov{e}{\alpha_1(n_1)}{\alpha_2(n_2)} + 2\delta.
  \end{equation*}
  Let $n_1 \geq m_1$ and $n_2 \geq m_2$.

@@

  If $p_1$ lies between $\alpha_2(n_2)$ and $p_1$ on $[\alpha_1(n_1),
  \alpha_2(n_2)]$ then, by considering the triangle with vertices $p_2$,
  $\alpha_2(m_2)$ and $\alpha_2(n_2)$, we see that $\dist(p_1, \alpha_2) \leq
  2\delta$. Therefore $\dist(\alpha_1(m_1), \alpha_2) \leq 3\delta$, and so
  \begin{equation*}
    \gromov{e}{\alpha_1(m_1)}{\alpha_2(m_2)} \geq \min\{m_1, m_2\} - 3\delta
  \end{equation*}
  and the result follows.

  Otherwise,
  \begin{equation*}
    \dist(\alpha_1(n_1), \alpha_2(n_2)) = \dist(\alpha_1(n_1), p_1) +
        \dist(p_1, p_2) + \dist(p_2, \alpha_2(n_2)).
  \end{equation*}
  Therefore,
  \begin{align*}
    \mathrlap{\gromov{e}{\alpha_1(n_1)}{\alpha_n(n_2)} - \gromov{e}{\alpha_1(m_1)}{\alpha_2(m_2)}}
    \quad\quad\phantom{{}={}}&\\
           &\mathllap{{}={}}\left(\dist(\alpha_1(m_1), \alpha_1(n_1)) - \dist(\alpha_1(m_1), p_1)\right) \\
           &+ \left(\dist(\alpha_1(m_1), \alpha_2(m_2)) - \dist(p_1, p_2)\right) \\
           &+ \left(\dist(\alpha_2(m_2), \alpha_2(n_2)) - \dist(p_2, \alpha_2(m_2))\right) \\
           &\mathllap{{}\leq{}} \delta+2\delta+\delta=4\delta 
  \end{align*}
  It follows that
  \begin{equation*}
    \gromov{e}{\alpha_1(\infty)}{\alpha_2(\infty)} \leq \gromov{e}{\alpha_1(m_1)}{\alpha_2(m_2)} + 6\delta,
  \end{equation*}
  which completes the proof.
\end{proof}

@@

  By definition of the visual metric, $\gromov{e}{\xi_1}{\xi_2} \geq
  \log_a(k_1/\rho_0)$. Therefore, by \cref{lem:boundary_gromov_product},
  \begin{equation*}
    \gromov{e}{\alpha_1(n)}{\alpha_2(n)} \geq \min\{n - 3\delta, \log_a(k_1/\rho_0) - 6\delta\}.
  \end{equation*}
  In particular,
  \begin{equation*}
    \dist(\alpha_1(n), \alpha_2(n)) \leq \max\{6\delta, 12\delta - 2(\log(k_1/\rho_0) - n)\}
  \end{equation*}
  and the result follows.
\end{proof}

@@

\begin{proof}
  By definition, $p^\infty_m(\xi)$ is contained in the simplex spanned by the set
  $\set{g \in S_m \suchthat \xi \in V_m(g)}$ and $p^n_m\composed p^\infty_n(\xi)$ is
  contained in the simplex spanned by $\{p^n_m(g) \suchthat g \in S_n \text{
  and } \xi \in V_n(g)\}$.  We show that the union
  \begin{equation*}
    \set{g \in S_m \suchthat \xi \in V_m(g)} \union \{p^n_m(g) \suchthat g \in S_n \text{ and } \xi \in V_n(g)\}
  \end{equation*}
  of these sets spans a simplex in $K_n$; this simplex then contains
  $p^\infty_m(\xi)$ and $p^n_m\composed p^\infty_n(\xi)$.  It is sufficient to
  prove that if $\xi \in V_m(g_1) \intersection V_n(g_2)$ for $g_1 \in S_m$ and
  $g_2 \in S_n$ then $\dist(g_1, p^n_m(g_2)) \leq D$.

@@

  The limit~\eqref{eqn:zi_closer_to_gi_than_x}, taken together with the fact
  that $\dist(g_i, x) = \dist(g_i, p_i) = n_i$, shows that the distances
  $\dist([z_i, g_i], x)$ and $\dist([z_i, g_i], p_i)$ tend to infinity as
  $i\to\infty$.  We now divide into cases according to which of $x$ and $p_i$
  is closer to $z_i$.
  \begin{enumerate}
    \item If $x$ is between $z_i$ and $p_i$ on $\alpha$ then by considering a
      geodesic triangle with vertices $g_i$, $z_i$ and $p_i$ we see that for
      $i$ sufficiently large, $x$ is within a distance $\delta$ of a point
      $q_i$ on the geodesic from $g_i$ to $p_i$.  Therefore,
      \begin{align*}
        \dist(g_i,x)&\leq \dist(g_i,q_i)+\delta\\
                        &\leq \dist(g_i,p_i)-\dist(p_i,q_i)+\delta\\
                        &\leq \dist(g_i,p_i)-\dist(x,p_i)+2\delta.
      \end{align*}
      It follows that $\dist(x,p_i) \leq \dist(g_i,p_i)-\dist(g_i,x)+2\delta
      = 2\delta$.
    \item If $p_i$ is between $z_i$ and $x$ on $\alpha$ then by an identical 
      argument with the r\^oles of $x$ and $p_i$ reversed we can similarly 
      deduce that 
      \begin{equation*}
        \dist(x,p_i)\leq\dist(g_i,x) - \dist(g_i,p_i) + 2\delta =2\delta.
      \end{equation*}
  \end{enumerate}

@@

  Since $g_i \to \xi$, the distance $\dist(v, [\xi, g_i]) \to \infty$ as
  $i\to\infty$. The triangle with vertices $\xi$, $g_i$ and $x$ is
  $\delta$-slim, so the geodesic path from $g_i$ to $x$ passes within a
  distance $\delta$ of $v$ for $i$ large enough. Therefore, since $\dist(g_i,
  x) = n_i$ for $i$ large enough, the following inequality holds for all $i$
  large enough.
  \begin{equation*}
    0 \leq \dist(g_i, v) + \dist(v, x) - n_i \leq 2\delta.
  \end{equation*}

@@

  We split into cases according to the order of $\xi$, $v'$ and $x'$ on
  $\alpha'$.
  \begin{enumerate}
    \item
      First we suppose that $v'$ is between $x'$ and $\xi$ on $\alpha'$. Then as
      in the argument above, for $i$ sufficiently large we have the following
      inequality:
      \begin{equation*}
        0 \leq \dist(g_i, v') + \dist(v', x') - n_i \leq 2\delta.
      \end{equation*}
      And therefore,
      \begin{equation*}
        -2\delta \leq \dist(g_i, v) + \dist(v, x') - n_i \leq 4\delta.
      \end{equation*}
      Finally, putting these inequalities together,
      \begin{equation*}
        \dist(v,x') \leq \dist(v,x) + 4\delta,
      \end{equation*}
      and thus we can uniformly bound this distance in this case.
    \item
      Alternatively, $x'$ is between $v'$ and $\xi$ on $\alpha'$ and so (since
      the triangle with vertices $\xi$, $v$ and $v'$ is $\delta$-slim) $x'$ is
      within a distance $2\delta$ of the geodesic ray from $x$ to $\xi$. By
      considering the triangle with vertices $\xi$, $g_i$ and $x$ for $i$ large
      enough, a geodesic segment from $g_i$ to $x$ passes within a distance
      $3\delta$ of $x'$. Therefore we have the following inequality for all $i$
      sufficiently large:
      \begin{equation*}
        0 \leq \dist(g_i, x') + \dist(x', x) - \dist(g_i, x) \leq 6\delta.
      \end{equation*}
      Finally, for $i$ sufficiently large, $\dist(g_i, x') = \dist(g_i, x) = n_i$,
      so
      \begin{equation*}
        \dist(x,x') \leq 6\delta.
      \end{equation*}
  \end{enumerate}
\end{proof}

@@

\begin{lemma}\label{lem:describing_q_i}\todo{Check this}
  Let $\zeta \in \boundary G - \set\xi$ and suppose that $q_i(\zeta) \in H_i$
  is defined, so $\zeta \in U_i$, and $N_{4\delta+1} q_i(\zeta) \in H_i$. Then
  $q_i(\zeta)$ is contained in the minimal simplex of $H_i$ with vertex set
  \begin{equation*}
    N_{2\delta+1} \set{\eta(n_i)\suchthat\text{$\eta$ a geodesic ray with
    $\eta(0) = g_i$ and $\eta(\infty) = \zeta$}}.
  \end{equation*}\qed
\end{lemma}

@@

\begin{lemma}\label{lem:propermaps} 
  For any compact subset $C \subset H$ there exists $i_0$ such that
  \begin{equation*}
    \bigunion_{i\geq i_0} q_i^{-1} C
  \end{equation*}
  is a relatively compact subset of $\boundary G - \set\xi$.
\end{lemma}

@@

\begin{restatable}{theorem}{ddagimpliesLCd}\label{thm:ddagimpliesLCd}
  If $G$ satisfies $\Sd_M$ for all $M$ then $\boundary G$ is locally simply
  connected.
\end{restatable}

@@

\begin{lemma}\label{lem:useful}
  Let $(x_n)$ be a sequence of points in $G$ with $\dist(x_{n+1}, e) = 
  \dist(x_n, e) + 1$ and $\dist(x_{n+1}, x_n)$ bounded. Then,
  \begin{equation*}
    \gromov{e}{x_m}{x_n} \geq \dist(e,x_m) - C
  \end{equation*}
  for some constant $C$ depending only on $\delta$ and the bound on 
  $\dist(x_{n+1}, x_n)$.
\end{lemma}

@@

  By the triangle inequality it follows that for $n\geq m$ we have the following 
  inequality.
  \begin{equation*}
    \vdistance(\alpha_n(\infty), \alpha_m(\infty)) \leq C_1 a^{-i_m}
  \end{equation*}
  for some constants $C_1$ depending only on $\delta$ and $C_0$. Then, by
  definition of the visual metric, there exists a constant $C_2$ such that
  \begin{equation*}
    \gromov{e}{\alpha_n(\infty)}{\alpha_m(\infty)} \geq i_m - C_2.
  \end{equation*}

  Now, by \cref{lem:boundary_gromov_product} there exists a constant $C_3$ such
  that
  \begin{equation*}
    \gromov{e}{\alpha_n(i_n)}{\alpha_m(i_m)} \geq i_m - C_3,
  \end{equation*}
  as required.
\end{proof}

\begin{lemma}\label{lem:linearproduct}
  There is a constant $C$ such that if $x \in \Skel_{d+1} K_m$ then
  \begin{equation*}
    \gromov{e}{i^m_n(x)}{x} \geq m - C
  \end{equation*}
  for all $n\geq m\geq n_0$.
\end{lemma}

@@

  We now bound the distance $\dist(y_n, y_{n+1}$. To start with, $\dist(y_n,
  i^n_{n+1} y_n) \leq \epsilon$. Let $R$ be such that any two vertices in the
  1-skeleton of $\sd^k \Delta^{d+1}$ are joined by a path traversing at most
  $R$ edges. Let $\sigma$ be the minimal simplex of $K_n$ containing
  $i^m_n(x)$. Then $y_n$ is a vertex of $\sigma$ and $y_{n+1}$ is a vertex of
  the image of $\sigma$ under $i^n_{n+1}$, so $\dist(i^n_{n+1} y_n, y_{n+1})
  \leq RD$.  Putting this together,
  \begin{equation*}
      \dist(y_n, y_{n+1}) \leq \epsilon + RD
  \end{equation*}

@@

  Finally, by applying the inequality in \cref{rem:dist_vs_newdist}, we deduce
  that
  \begin{equation*}
      \gromov{e}{i^m_n(x)}{x} \geq m - C - 3D.\qedhere
  \end{equation*}
\end{proof}

@@

\begin{lemma}\label{lem:simplexproduct}
  There is a constant $C$ such that if $m \geq n_0$ and $x$ and $y$ are in a
  common simplex of $\Skel_{d+1} K_m$ then
  \begin{equation*}
    \gromov{e}{i^m_n(x)}{i^m_n(y)} \geq m - C
  \end{equation*}
  for all $n\geq m$.
\end{lemma}

@@

\begin{proposition}\label{prop:basic_homotopies}
  Let $C$ be a constant. Then there exists a number $m_0$ and a function $\mu
  \from \posreals\to\posreals$ such that $\mu(\eta)\to0$ as $\eta\to0$ with the following
  property. Let $n \geq m_0$ and let $f_0$ and $f_1$ be any maps from
  $\boundary\Delta^{d+1}$ to $K_n$ satisfying the following conditions:
  \begin{enumerate}
    \item the maps $f_0$ and $f_1$ are affine on some subdivision of
      $\boundary\Delta^{d+1}$;
    \item for any $x \in \boundary\Delta^{d+1}$, the distance 
      $\newdist(f_0(x), f_1(x))$ is at most $C$;
    \item each of $f_0$ and $f_1$ admits a factoring.
  \end{enumerate}
  Then there is a homotopy $h$ from $i^n_\infty\composed f_0$ to
  $i^n_\infty\composed f_1$ satisfying a uniform continuity condition: for any
  $x \in \boundary\Delta^{d+1}$ and any $s$ and $t$ in $[0,1]$,
  \begin{equation*}
    \rho(h(x,s), h(x,t)) \leq \mu(\abs{s-t})a^{-n}.
  \end{equation*}
\end{proposition}

@@

  Let $n \geq m_0$.  Let $J$ be a subdivision of $\boundary\Delta^{d+1}$ such
  that $f_0$ and $f_1$ are both affine on $J$. Then the map 
  \begin{equation*}
    f_0 \disjointunion f_1 \from J \times \{0\} \disjointunion J \times \{1\}
          \to K_n,
  \end{equation*}
  defined on a subset of the product simplicial complex $J \times [0,1]$,
  satisfies the conditions of \cref{prop:extendingaffinemaps2}, and so admits
  an affine extension $F \from \sd^{k'} (J \times [0,1]) \to K_n$. Let $h =
  i^n_\infty \composed F$, so $h$ is a homotopy from $i^n_\infty\composed f_0$
  to $i^n_\infty\composed f_1$ and it remains to prove the uniform continuity
  assertion.

@@

\begin{proof}
  Let $\xi \in \boundary G$. By \cref{lem:linearproduct} there is a 
  constant $C$ such that 
  \begin{equation*}
    \gromov{e}{i^m_n\composed p^\infty_m(\xi)}{p^\infty_m(\xi)} \geq m - C
  \end{equation*} 
  for each $n\geq m\geq n_0$.
